---
title: "Dwarves & Giants - no audio data pipeline"
output: html_notebook
---
```{r}
getwd()
file.exists('/Users/mdavistr/Desktop/dwarves&giants/dg_pipeline/111.csv')
list.files('dg_pipeline')
dir.exists('dg-pipeline')
normalizePath("dg_pipeline")
```

Loading CSVs
111111 = Molly's trial run of the prototype
Creates a practice df
Creates a trials df
```{r}
data = read.csv('/Users/mdavistr/Desktop/dwarves&giants/dg_pipeline/111.csv')
nrow(data)
library(tidyverse)
MollyShortPractice <- data %>% 
  slice(-(1:6)) %>%
  slice((1:23)) %>%
  select(prac_numbers, practicenumbers.started, trials.practicenumbers_resp.keys,trials.practicenumbers_resp.rt)
head(MollyShortPractice)
view(MollyShortPractice)

MollyShortTrials <- data %>% 
  slice(-(1:30)) %>%
  slice(-n()) %>%
  select(numbers, monitornumbers.started, trials_2.monitornumbers_resp.keys,trials_2.monitornumbers_resp.rt)
head(MollyShortTrials)
view(MollyShortTrials)
```
Now to see how well she did overall
Doing practice first 

```{r}
library(dplyr)
library(tidyr)

MollyShortPracticeClean <- MollyShortPractice %>%
  mutate(
    trials.practicenumbers_resp.keys = gsub("\\[|\\]|'", "", trials.practicenumbers_resp.keys),  
    trials.practicenumbers_resp.rt = gsub("\\[|\\]|'", "", trials.practicenumbers_resp.rt),
    response_keys = strsplit(trials.practicenumbers_resp.keys, ", "),  # Split multiple presses
    response_rts = strsplit(trials.practicenumbers_resp.rt, ", "),
    first_rt = sapply(response_rts, function(x) ifelse(length(x) > 0, as.numeric(x[1]), NA)),  # Extract first RT
    second_rt = sapply(response_rts, function(x) ifelse(length(x) > 1, as.numeric(x[2]), NA)),
    first_press = sapply(response_keys, function(x) ifelse(length(x) > 0, x[1], NA)),  # Extract first press
    second_press = sapply(response_keys, function(x) ifelse(length(x) > 1, x[2], NA)), # Extract second press
    correct = as.numeric(first_press) == prac_numbers,
    correct2 = as.numeric(second_press) == prac_numbers# Check if first press matches practice number
  ) %>%
  select(prac_numbers, practicenumbers.started, first_press, second_press, first_rt, second_rt, correct, correct2, trials.practicenumbers_resp.rt)
view(MollyShortPracticeClean)

```

```{r}
MollyShortTrialsClean <- MollyShortTrials %>%
  mutate(
    trials_2.monitornumbers_resp.keys = gsub("\\[|\\]|'", "", trials_2.monitornumbers_resp.keys),  
    trials_2.monitornumbers_resp.rt = gsub("\\[|\\]|'", "",  trials_2.monitornumbers_resp.rt),
    response_keys = strsplit(trials_2.monitornumbers_resp.keys, ", "),  # Split multiple presses
    response_rts = strsplit( trials_2.monitornumbers_resp.rt, ", "),
    first_rt = sapply(response_rts, function(x) ifelse(length(x) > 0, as.numeric(x[1]), NA)),  # Extract first RT
    second_rt = sapply(response_rts, function(x) ifelse(length(x) > 1, as.numeric(x[2]), NA)),
    first_press = sapply(response_keys, function(x) ifelse(length(x) > 0, x[1], NA)),  # Extract first press
    second_press = sapply(response_keys, function(x) ifelse(length(x) > 1, x[2], NA)), # Extract second press
    correct = as.numeric(first_press) == numbers,
    correct2 = as.numeric(second_press) == numbers# Check if first press matches practice number
  ) %>%
  

  select(numbers, monitornumbers.started, first_press, second_press, first_rt, second_rt, correct, correct2, trials_2.monitornumbers_resp.rt)
view(MollyShortTrialsClean)

write.csv(MollyShortTrialsClean, "MollyShortTrialsClean.csv", row.names = FALSE)
```
Now I'm trying to figure out how long it took Molly to do the task
Match data press to most recent presentation of that number
Add RTs

#######
```{r}
MollyShortTrialsClean$MonitorRT <- MollyShortTrialsClean$monitornumbers_started
MollyShortTrialsClean$MonitorRT[MollyShortTrialsClean$first_press == MollyShortTrialsClean$numbers] <-   MollyShortTrialsClean$monitornumbers_started[MollyShortTrialsClean$first_press == MollyShortTrialsClean$numbers] + MollyShortTrialsClean$first_rt[MollyShortTrialsClean$first_press == MollyShortTrialsClean$numbers]
view(MollyShortTrialsClean)



MollyShortTrialsClean$MonitorRT <- ifelse(MollyShortTrialsClean$first_press == MollyShortTrialsClean$numbers,
                                           MollyShortTrialsClean$monitornumbers_started + MollyShortTrialsClean$first_rt,
                                           MollyShortTrialsClean$monitornumbers_started)
```

Manipulated CSV, manually added RTs
```{r}
ADDEDRT = read.csv('/Users/mdavistr/Desktop/dwarves&giants/dg_pipeline/MollyShortTrialsCleanADDEDRT.csv')
#view(ADDEDRT)

ADDEDRT$matches <- as.numeric(ADDEDRT$matches)

filtered_data <- ADDEDRT$matches[!is.na(ADDEDRT$matches)]
min_value <- min(filtered_data)
max_value <- max(filtered_data)

# Print the min and max values
cat("Minimum value:", min_value, "\n")
cat("Maximum value:", max_value, "\n")

hist(ADDEDRT$matches, breaks = 50, main="Histogram of RT (correct)", xlab="RT(s)", col="lightblue", border="black")

```

```{r}
#install.packages("dplyr")
#library(dplyr)
#ADDEDRT$first_press <- as.numeric(ADDEDRT$first_press)
#hist(ADDEDRT$first_press, breaks = 9, main="Histogram of Numbers Pressed", xlab="Number Keys", col="lightblue", border="black", plot =FALSE)

monitor_counts <- table(ADDEDRT$first_press)


# Print the counts
print(monitor_counts)

ignore_counts <- table(ADDEDRT$numbers)

# Print the counts
print(ignore_counts)
```
Total number presses = 98
Errors in presses = 19
Total opportunities = 125
79/125
Percent Correct = .632

Correctly Skipped = 75
75/75
79+75/125+75 = .77


Need to index and compare to each choice
update each curr, etc each time I have a new button press to compare to numbers
```{r}
#for (i in 1:nrow(ADDEDRT)) {
#  print(paste("Row:", i, "Value:", ADDEDRT[i, 1]))
#}

ADDEDRT$TotalRT <- rep(NA, nrow(ADDEDRT))

for (i in 3:nrow(ADDEDRT)) {
  current_value <- ADDEDRT[i, 3]
  current_numStart <- ADDEDRT[i, 2]
  current_rt <- ADDEDRT[i,5]
  same_row <- (current_value == ADDEDRT[i, 1])
  prev_row <- (current_value == ADDEDRT[i - 1, 1])
  two_rows_before <- (current_value == ADDEDRT[i - 2, 1])
  
  if (current_value == as.numeric(ADDEDRT[i, 1])) {
    ADDEDRT$TotalRT[i] <- current_rt
  } 
  if (current_value == as.numeric(ADDEDRT[i - 1, 1])) {
    matched_stim_time <- as.numeric(ADDEDRT[i - 1, 2])  # Previous row
    ADDEDRT$TotalRT[i] <- (current_numStart - matched_stim_time) + current_rt
  } 
  if (current_value == as.numeric(ADDEDRT[i - 2, 1])) {
    matched_stim_time <- as.numeric(ADDEDRT[i - 2, 2])  # Two rows before
    ADDEDRT$TotalRT[i] <- (current_numStart - matched_stim_time) + current_rt
  }
}
```

